Guidelines for reliable and reproducible functional enrichment analysis

### 2021-08-29 analysis.Rmd
Assed QC2 data with resolved discrepancies. Added ORA combined vs separate and GSEA parameters.

png("images/assumptions1.png")
par(mar=c(5,12,3,1))
barplot(tail(res,20),horiz=TRUE,las=1,cex.names = 1, xlab="no. analyses",
        main = "Assumptions violated", xlim=c(0,100))
text(y = (1:length(res)*1.2)-0.75  , x = res+100, label = res, pos = 3, cex = 1, col = "black")
grid()
dev.off()

>>>>

png("images/assumptions1.png")
par(mar=c(5,12,3,1))
barplot(tail(res,20),horiz=TRUE,las=1,cex.names = 1, xlab="no. analyses",
        main = "Assumptions violated", xlim=c(0,1500))
text(y = (1:length(res)*1.2)-0.75  , x = res+80, label = res, pos = 3, cex = 1, col = "black")
grid()
dev.off()

### 2021-08-29 manuscript.Rmd
Assed QC2 data with resolved discrepancies. Added ORA combined vs separate and GSEA parameters.

@@

@@

@@

@@

>>>>

Felisbino, M. B., Ziemann, M., Khurana, I., Okabe, J., Al-Hasani, K., Maxwell, S., … El-Osta, A. (2021). Valproic acid influences the expression of genes implicated with hyperglycaemia-induced complement and coagulation pathways. Scientific Reports, 11(1), 2163.

@@

Jassal, B., Matthews, L., Viteri, G., Gong, C., Lorente, P., Fabregat, A., … D’Eustachio, P. (2020). The reactome pathway knowledgebase. Nucleic Acids Research, 48(D1), D498–D503.

@@

Love, M. I., Huber, W., & Anders, S. (2014). Moderated estimation of fold change and dispersion for RNA-seq data with DESeq2. Genome Biology, 15(12), 550.

@@

Yu, G., Wang, L.-G., Han, Y., & He, Q.-Y. (2012). clusterProfiler: an R package for comparing biological themes among gene clusters. Omics: A Journal of Integrative Biology, 16(5), 284–287.

@@

Ziemann, M., Kaspi, A., & El-Osta, A. (2019). Digital expression explorer 2: a repository of uniformly processed RNA sequencing data. GigaScience, 8(4). doi:10.1093/gigascience/giz022
